Dynamic Transition Analysis with TIMES

### 2019-01-13 doc/2019-01-poster/poster.tex
changed cost plot's size
Former-commit-id: 5820c1553bfd56210cdea02007787819f60cb187 [formerly d56758327126644dc6679439d39c83f24b13233d]
Former-commit-id: d77443d12d2af53eb7c755a745163a88b2e79b1b
changed limitations
Former-commit-id: 956028773ff0e17257623b287fba622807fe26f1 [formerly c894042215b115d74fe4d924b3065ca9c7d1a613]
Former-commit-id: eea32f176fe0496ef623bd534df81467ea4a9558
reduced text, made plots larger

\begin{description}
{\large 
        \item[\textbf{Division:}] Energy Analysis Division
        \item[\textbf{Project:}] I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions
        \item[\textbf{Objective:}] Evaluate potential impact of novel energy technologies within Japan's energy system.
\item[\textbf{Milestones:}] ~\\}
        \begin{itemize}
        \item Minimize carbon emissions within realistic constraints.
        \item Optimize realistic 2010-2050 decarbonization roadmaps.
	\item Identify high impact technologies.
        \item Identify potential transition bottlenecks.
        \item Help Japan's policymakers create timelines for R\&D investment and infrastructure development.
        \item Quantify system sensitivity to technology readiness.
	\item Predict impediments to strategically optimal technology deployment.
	\end{itemize}
\end{description}

@@

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
We are simulating \textbf{dynamic} transition scenarios 
\cite{pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\

Our model includes conventional energy sources such as \textbf{fossil fuels, nuclear, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}. \hfill \break

@@

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nuc_elc}
\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
\label{s1e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nuc_co2}
\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
\label{s1c}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nonuc_elc}
\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
\label{s2e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nonuc_co2}
\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
\label{s2c}
\end{figure}

@@

\begin{column}{\onecolwid} % The second column

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function is solved within user defined constraints.\\
\textbf{Key assumptions:}

\begin{itemize}
        \item\textbf{Objective function:} System cost.

         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year) \cite{noauthor_electricity_2017}.

         \item Hydropower capacity held constant \cite{noauthor_energy_2018}.

         \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant. Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig. \ref{cost}.

@@

         \item Growth rate and maximum annual increase in capacity of nuclear, wind and solar is based on data and trends seen in USA, China, and Japan. \cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}

         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with its costs reducing by 2050 as per projected trends. \cite{kato_energy_2016}

         \item \textbf{Hydrogen production:} Steam reforming deployed in 2030. Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies. \cite{kato_energy_2016} \cite{acar_comparative_2014} \\

 \end{itemize}

We have modeled \textbf{four scenarios} with different energy technologies enabled: \hfill \break

\begin{tabular}{c c c c c}

\textbf{Scenario} & \textbf{Figures}         & \textbf{Conventional}      & \textbf{I$^2$CNER}   & \textbf{New nuclear} \\
                  &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
1                 & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
2                 & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
3                 & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
4                 & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
\end{tabular}

@@

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{legend}
%\caption{Legend}
\label{legend}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nuc_elc}
\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
\label{s3e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nuc_co2}
\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
\label{s3c}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nonuc_elc}
\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
\label{s4e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nonuc_co2}
\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
\label{s4c}
\end{figure}

@@

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------
\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{cost}
\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
\label{cost}
\end{figure}
         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy supply.

                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience.

                \item Photocatalytic H$_2$ and offshore wind can meet I$^2$CNER targets in the absence of nuclear, but at significantly higher cost.

                \item Technologies with the highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
	\end{itemize}
        \end{alertblock}

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Future work}
    \begin{itemize}

    \item Capture realistic, gradual transition behaviour.

@@

    \item Sensitivity analysis to maximize impact of I$^2$CNER technology.

    \item Detailed cost analysis

    \item Incorporation of natural gas and/or energy storage technologies to supplement renewable energy and I$^2$CNER technology.

>>>>

\begin{description}
{%\large 
        \item[\textbf{Division:}] Energy Analysis Division
        \item[\textbf{Project:}] I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions
        \item[\textbf{Objective:}] Evaluate potential impact of novel energy technologies within Japan's energy system.
\item[\textbf{Milestones:}] ~\\}
        \begin{itemize}
        \item Minimize carbon emissions within realistic constraints.
        \item Create realistic decarbonization roadmaps.
	    \item Identify high impact technologies.
        \item Identify potential transition bottlenecks.
        %\item Help create timelines for R\&D investment and infrastructure development.
     	\end{itemize}
\end{description}

@@

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{kikuchi_simulation-based_2017,pambudi_impact_2017}.  
We are simulating \textbf{dynamic} transition scenarios 
\cite{pfenninger_energy_2014} aimed at \textbf{optimizing energy supply} to minimize carbon 
emissions in Japan to 80\% of 1990 levels by 2050.
Our model has conventional and I$^2$CNER technologies (\textbf{carbon capture(CCS)} \& \textbf{H$_2$} production).
\end{block}

@@

\begin{figure}[H] 
\centering
\includegraphics[scale=1.1]{legend}
%\caption{Legend}
\label{legend}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.51]{conv_nuc_elc}
\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
\label{s1e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.51]{conv_nuc_co2}
\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
\label{s1c}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.51]{conv_nonuc_elc}
\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
\label{s2e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.51]{conv_nonuc_co2}
\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
\label{s2c}
\end{figure}

@@

%----------------------------------------------------------------------------------------
\begin{column}{\onecolwid} % The second column
%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear \& mixed-linear algorithms. An objective 
        function is solved within given constraints.\\
\textbf{Key assumptions:}
\begin{itemize}
        \item\textbf{Objective function:} System cost \ref{cost}.

         \item\textbf{Constraints:} CO$_2$ emissions, demand(+1.7\% per year) \cite{noauthor_electricity_2017}.

         \item Hydropower and geothermal capacity are constant \cite{noauthor_energy_2018}.

@@

         \item Nuclear, wind, solar growth rate based on trends in USA, China, and Japan.\cite{noauthor_electricity_2017,noauthor_energy_2018,eia_international_nodate,eia_monthly_2018,iea-pvps_snapshot_2018}

         \item \textbf{CCS:} Deploys in 2030,costs reduce by 2050. \cite{kato_energy_2016}

         \item \textbf{H$_2$:} Steam reforming deploys in 2030. Photocatalytic H$_2$ deploys in 2050, assumed cost-competitive. \cite{kato_energy_2016} \cite{acar_comparative_2014} \\         
 \end{itemize}

We have modeled \textbf{four scenarios}:\hfill \break

\begin{tabular}{| c | c | c | c | c |}
\hline
\textbf{Scenario}& \textbf{Figures}&\textbf{Conventional}&\textbf{I$^2$CNER}&\textbf{New nuclear}\\
                 &             &\textbf{technology}&\textbf{technology}&\textbf{reactors}\\
                  \hline
1               & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
2               & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
3               & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
4               & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
\hline
\end{tabular}
\end{block}

@@

\begin{figure}[H] 
\centering
\includegraphics[scale=1.62]{i2cner_nuc_elc}
\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
\label{s3e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.62]{i2cner_nuc_co2}
\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
\label{s3c}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.62]{i2cner_nonuc_elc}
\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
\label{s4e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.62]{i2cner_nonuc_co2}
\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
\label{s4c}
\end{figure}

@@

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------
\begin{figure}[H] 
\centering
\includegraphics[scale=1.4]{cost}
\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
\label{cost}
\end{figure}
         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power is the cleanest and cheapest.

                \item Without nuclear and I$^2$CNER, solar and wind are deployed in a 1:2 ratio.

                \item H$_2$ and wind can meet I$^2$CNER targets without nuclear, at high cost.

                \item Highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$, solar
	\end{itemize}
        \end{alertblock}

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Limitations and Future work}
    \begin{itemize}

    \item Model focuses on \textbf{electricity supply sector}.

    \item Cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is constant.

    \item Emissions tied to energy production, not capacity installation.

    \item Annual timestep can't capture variation in wind, solar.

    \item Capture realistic transitions and fluctuations in demand.

@@

    \item Sensitivity and cost analysis to maximize I$^2$CNER's impact.

    %\item Detailed cost analysis

    \item Add energy storage to supplement renewables and H$_2$.
